Detecting Facial Expressions in Professional Tennis Matches

### 2017-09-11 Report06-12.Rmd
Converted data dense graphics to png with dpi 300

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)
library(gridExtra)
library(ggmosaic)
library(tidyverse)
library(purrr)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)

@@

```{r Trial-Image, fig.cap = "This image of Bernard Tomic was chosen as a trial image to be presented to each of the software before they were included in the research. It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE}
imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
overlayGgplot(imagesList0, aminFaces, matchBox = FALSE)
```

@@

```{r timeTable, results='asis', fig.cap="System time taken by the four APIs to finish searching individual images, plotted against number of faces discovered. Skybiometry is the fastest, and Microsoft is the slowest. The largest variability is when no faces are found.\\label{tab:timeTable}"}

@@

```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API. The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}"}

@@

```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual. The top left image presents a potential faces that actually defines an area containing a player's back and a ball boy's torso. The top right shows two potential faces that are actually the KIA logo on the net. The bottom left image was very interesting as the player's face was found, but the shirts of both the player and ball boy were deemed potential faces. The bottom right image had a lot more faces that usually recognised. Animetrics found a fist to the right on the centre that it considered a potential face. \\label{fig:UnusualImages}" }
i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image a.")
i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image b.")
i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image c.")
i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image d.")

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)
library(gridExtra)
library(ggmosaic)
library(tidyverse)
library(purrr)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=FALSE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)

@@

```{r Trial-Image, fig.cap = "This image of Bernard Tomic was chosen as a trial image to be presented to each of the software before they were included in the research. It was expected that the software would be able to find this face, despite the player facing away from the camera.\\label{fig:Trial-Image}", message=TRUE, warning=TRUE, dev="png", dpi=300}
imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
overlayGgplot(imagesList0, aminFaces, matchBox = FALSE)
```

@@

```{r timeTable, results='asis', fig.cap="System time taken by the four APIs to finish searching individual images, plotted against number of faces discovered. Skybiometry is the fastest, and Microsoft is the slowest. The largest variability is when no faces are found.\\label{tab:timeTable}", dev="png", dpi=300}

@@

```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API. The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}", dev="png", dpi=300}

@@

```{r UnusualImages, fig.cap = "Animetrics provided many results that were quite unusual. The top left image presents a potential faces that actually defines an area containing a player's back and a ball boy's torso. The top right shows two potential faces that are actually the KIA logo on the net. The bottom left image was very interesting as the player's face was found, but the shirts of both the player and ball boy were deemed potential faces. The bottom right image had a lot more faces that usually recognised. Animetrics found a fist to the right on the centre that it considered a potential face. \\label{fig:UnusualImages}", dev="png", dpi=300}
i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image a.")
i2 <- "2016_HSA_R03_FDelbonis_ARG_vs_GSimon_FRA_MS302_clip.0072.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image b.")
i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image c.")
i4 <- "2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png" %>% overlayGgplot(., legend=FALSE) + ggtitle("  Image d.")
